What do incoming university students believe about open science practices in

### 2021-10-06 analysis/Manuscript.Rmd
Formatting fixes as per email

---
title: What do incoming university students believe about open science practices in
  psychology?
author:
- name: Jennifer L. Beaudry
  affiliation: '1'
  corresponding: yes
  address: Postal address
  email: jbeaudry@swin.edu.au
  role: null
- name: Michael C. Philipp
  affiliation: '2'
  role: null
- name: Matt N. Williams
  affiliation: '2'
  role: null
- name: Emily Kothe
  affiliation: '3'
  role: null
shorttitle: Psychology students' beliefs about open science
output:
  papaja::apa6_word: default
  papaja::apa6_pdf: default
authornote: |
  1 Flinders University, Australia
  2 Massey University, New Zealand
  3 Deakin University, Australia
abstract: |
## BACKGROUND: Understanding students’ naive conceptions about how science works and the norms that guide scientific best practice is important so that teachers can adapt their teaching to the students’ existing understandings. 
## OBJECTIVE: To describe what incoming undergraduate students of psychology believe about reproducibility and open science practices in psychology. 
## METHOD: International online survey with participants who were about to start their first course in psychology (N = 239) .
## RESULTS: When asked about how research *should* be done, most students endorsed most (but not all) of ten open science practices. When asked to estimate the proportion of published psychological studies that apply each of a set of 10 open science practices, participants' estimates tended to average near 50%. Only 18% of participants had heard of the term "replication crisis".
## CONCLUSION: Despite relatively significant media attention on the replication crisis, few incoming psychology students are familiar with the term. Incoming students nevertheless appear to be sympathetic toward most open science practices, although they may overestimate the prevalence of these practices in psychology.
## TEACHING IMPLICATIONS: Teaching materials aimed at incoming psychology students should not assume pre-existing knowledge about open science or replicability.

keywords: open science, psychology, teaching, reproducibility, replication
wordcount: X
bibliography: ['r-references.bib','Undergrads & Open Science (public).bib']
floatsintext: yes
figurelist: no
tablelist: no
footnotelist: no
linenumbers: yes
mask: yes
draft: no
documentclass: apa6
classoption: man
affiliation:
- id: '1'
  institution: Swinburne University of Technology
- id: '2'
  institution: Massey University
editor_options: 
  chunk_output_type: console
---

@@

Rapid changes in methodological practice and empirical findings present significant pedagogical challenges for the teacher of psychology. Keeping textbooks and other instructional materials up to date is difficult when supposedly well-established findings are contradicted by new replications emerging at a rapid pace. Furthermore, training in emerging methodological practices is crucial for graduate students who may go on to apply psychological research methods themselves. Even for students who do not go on to conduct research themselves, an understanding of contemporary methodological practices - and problems with methodological practices in psychology - is essential for becoming informed and critical consumers of psychological knowledge. Studies have therefore begun to explore strategies for educating psychology students about replicability and open science practices [e.g., @chopikHowWhetherTeach2018; @graheHarnessingUndiscoveredResource2012; @jekelHowTeachOpen2020; @schonbrodtTrainingStudentsOpen2019]. These initiatives may help ingrain open science norms and change attitudes about research practices, but we know little about what these students know or believe about open science research practices prior to entering the university classroom. There are several reasons why this knowledge could be useful.

@@

There were 20 scenarios in total (see Table \@ref(tab:norm_counternorm_items)). Participants rated their agreement with each prescriptive statement on a 1 (strongly disagree) to 5 (strongly agree) scale.

<!-- Add Table X of norms and counternorms statements that map to each practice 
MW: The table captions/crossreferences may not be working - see the compiled document.
-->

```{r norm_counternorm_items}

@@

  "Practice" = c("critical", "critical", "HARKing", "HARKing", "Info for replicability", "Info for replicability",

@@

@@

We also sought to measure participants' normative beliefs about how psychological science is actually conducted by researchers around the world. To that end we asked participants, "When you consider all of the psychology studies conducted globally each year, what percentage of them would have the following characteristics?" These practices corresponded approximately to the ten norm-counternorm pairs described above, albeit with one norm excluded on the basis of not referring to externally observable behaviour (critically evaluating published studies vs. accepting them), and one practice added out of interest (data sharing on request).  (see Table XX). Participants were given a slider bar ranging from 0% to 100% to record their estimate.

@@

```{r norms_in_practice_items}
practice_items = data.frame(
  "Practice" = c("Preregistration", "Registered reports", "p-hacking", "HARKing", "Info for replicability",
                 "Preprint", "open materials", "Open data", "Data on request", "Open access"),
  "Item" = c("The plan for collecting and analysing data for the study is posted in an online registry before data collection starts",
             "A plan for the study is submitted to a journal to be checked by experts (peer reviewed) before the data is collected and analysed",
             "The researchers run many different analyses of the data, and report only those that produce interesting findings",
             "The researchers describe their results as if they predicted those results from the beginning, even if that isn’t actually true",
             "The researchers provide enough practical detail in their written report that another researcher could fully repeat (replicate) their study without needing to ask any questions of the original researchers",
             "A manuscript describing the findings of the study is posted openly online as soon as it is complete, even if the manuscript has not yet been checked by experts (peer reviewed) and accepted for publication in a journal",
             "The written materials and measures for the study are posted openly online so that other researchers and members of the public can access and use them",
             "Once the study is published, the anonymous responses from participants are posted openly online so that anyone can access and use the responses in their own research",
             "Once the study is published, the anonymous responses from participants are available to other researchers on request",
             "The research report describing the study and its findings is published in a journal that is free for anyone to access")
)

@@

Participants' beliefs about the replicability of results in psychological science were indexed by two questions. The first asked participants to, 
> "Imagine that a set of researchers selected 100 published studies about psychology, and repeat each study again, exactly how it was described in the original report but with a new set of participants. We call repeating a study like this a 'replication study.' At a guess, how many of these replication studies do you think would produce the same conclusions as the original studies?”

@@

In line with our preregistered analysis plan, we calculated the difference in means
between responses to each norm item and its accompanying counternorm, along with 
95% confidence intervals. For this analysis, we removed three cases with missing values. 
Table XX displays the means and standard deviations for each norm, counternorm, 
and the difference values.

@@

```{r difference between norm and counternorm}

@@

# breadcrumbs:
# need to figure out whether I can rotate a page in papaja
# I need to use apa_tables.... (in line with papaja)
# update practice descriptions so they make sense to readers

@@

<!-- I imagine we will remove the p.value column, but we might want this for now.  -->

## Norms in practice
Participants were also asked to estimate the proportion of psychology studies globally that apply each of ten practices. For many of these practices, participants’ estimates were near the midpoint of 50%. This said, participants perceived some practices as being applied relatively infrequently: For example, the mean estimate of the prevalence of HARKing, preprint sharing before publication, and open data sharing were all near 30%. Participants perceived the most common practice was providing enough information in written reports to permit replication without asking any questions of the original researchers.

```{r norms in practice}

@@

@@

Participants' estimates of the replicability of psychological studies were variable. The mean, _M_ =`r mean(df$rep_perc, na.rm = TRUE)` was near the midpoint of 50%, but with substantial variability around this estimate, _SD_ = `r sd(df$rep_perc, na.rm = TRUE)`, minimum = `r min(df$rep_perc, na.rm = TRUE)`,  maximum = `r max(df$rep_perc, na.rm = TRUE)`. A histogram of participants' responses is provided in Figure X.

```{r rep_perc_histogram}
hist(df$rep_perc, main = NULL, xlab = "Percentage")
```
_Figure X_. Histogram of participants' responses to the question: "Imagine that a set of researchers select 100 published studies about psychology, and repeat each study again, exactly how it was described in the original report but with a new set of participants. We call repeating a study like this a “replication study”. At a guess, how many of these replication studies do you think would produce the same conclusions as the original studies?" Responses provided on a visual slider.

@@

Figure XX displays the histograms for each of the norms in practice items.

```{r norms in practice histogram}

p <- in_prac_long %>%
  ggplot(aes(x = `prevalence rating`)) +
  geom_histogram(aes(y=stat(count)), binwidth = 10) +
    xlab("Prevalence Ratings (%)") +
    ylab("Frequency") +
    theme_classic () +
    theme(axis.text = element_text(size = 9), axis.title = element_text(size = 9)) +
    facet_wrap(~practice, nrow = 2)
p

#[breadcrumb: need to update the theme & the practice names]

@@

<!-- This is nice to do, but it generate a 150+ word paragraph of citations to packages, including citations to packages our code doesn't directly use (e.g. nlme, multilevel, etc.). We might need to cut it down manually to a more concise list?
-->

>>>>

---
title: What do incoming university students believe about open science practices in
  psychology?
author:
- name: Jennifer L. Beaudry
  affiliation: '1'
  corresponding: yes
  address: Postal address
  email: jbeaudry@swin.edu.au
  role: null
- name: Michael C. Philipp
  affiliation: '2'
  role: null
- name: Matt N. Williams
  affiliation: '2'
  role: null
- name: Emily Kothe
  affiliation: '3'
  role: null
shorttitle: Psychology students' beliefs about open science
output:
  papaja::apa6_word: default
  papaja::apa6_pdf: default
authornote: |
  1 Flinders University, Australia
  2 Massey University, New Zealand
  3 Deakin University, Australia
abstract: |
## BACKGROUND: Understanding students’ naive conceptions about how science works and the norms that guide scientific best practice is important so that teachers can adapt their teaching to the students’ existing understandings. 
## OBJECTIVE: To describe what incoming undergraduate students of psychology believe about reproducibility and open science practices in psychology. 
## METHOD: International online survey with participants who were about to start their first course in psychology (N = 239) .
## RESULTS: When asked about how research *should* be done, most students endorsed most (but not all) of ten open science practices. When asked to estimate the proportion of published psychological studies that apply each of a set of 10 open science practices, participants' estimates tended to average near 50%. Only 18% of participants had heard of the term "replication crisis".
## CONCLUSION: Despite relatively significant media attention on the replication crisis, few incoming psychology students are familiar with the term. Incoming students nevertheless appear to be sympathetic toward most open science practices, although they may overestimate the prevalence of these practices in psychology.
## TEACHING IMPLICATIONS: Teaching materials aimed at incoming psychology students should not assume pre-existing knowledge about open science or replicability.
keywords: open science, psychology, teaching, reproducibility, replication
wordcount: X
bibliography: ['r-references.bib','Undergrads & Open Science (public).bib']
floatsintext: yes
figurelist: no
tablelist: no
footnotelist: no
linenumbers: yes
mask: yes
draft: no
documentclass: apa6
classoption: man
affiliation:
- id: '1'
  institution: Swinburne University of Technology
- id: '2'
  institution: Massey University
- id: '3'
  institution: Deakin University, Geelong, Australia, Misinformation Lab, School of Psychology
editor_options: 
  chunk_output_type: console
csl               : "apa.csl" 
---

@@

Rapid changes in methodological practice and empirical findings present significant pedagogical challenges for the teacher of psychology. Keeping textbooks and other instructional materials up to date is difficult when supposedly well-established findings are contradicted by new replications emerging at a rapid pace. Furthermore, training in emerging methodological practices is crucial for graduate students who may go on to apply psychological research methods themselves. Even for students who do not go on to conduct research themselves, an understanding of contemporary methodological practices – and problems with methodological practices in psychology – is essential for becoming informed and critical consumers of psychological knowledge. Studies have therefore begun to explore strategies for educating psychology students about replicability and open science practices [e.g., @chopikHowWhetherTeach2018; @graheHarnessingUndiscoveredResource2012; @jekelHowTeachOpen2020; @schonbrodtTrainingStudentsOpen2019]. These initiatives may help ingrain open science norms and change attitudes about research practices, but we know little about what these students know or believe about open science research practices prior to entering the university classroom. There are several reasons why this knowledge could be useful.

@@

There were 20 scenarios in total (see Table \@ref(tab:normcounternormitems)). Participants rated their agreement with each prescriptive statement on a 1 (strongly disagree) to 5 (strongly agree) scale.

<!-- Add Table X of norms and counternorms statements that map to each practice 
MW: The table captions/crossreferences may not be working - see the compiled document.

EK: for cross-referencing to work you can't have underscores in the chunk name
-->

```{r normcounternormitems}

@@

  "Practice" = c("Critical thinking", "Critical thinking", "HARKing", "HARKing", "Info for replicability", "Info for replicability",

@@

\

@@

We also sought to measure participants' normative beliefs about how psychological science is actually conducted by researchers around the world. To that end we asked participants, "When you consider all of the psychology studies conducted globally each year, what percentage of them would have the following characteristics?" These practices corresponded approximately to the ten norm-counternorm pairs described above, albeit with one norm excluded on the basis of not referring to externally observable behaviour (critically evaluating published studies vs. accepting them), and one practice added out of interest (data sharing on request).  (see Table \@ref(tab:normsinpracticeitems)). Participants were given a slider bar ranging from 0% to 100% to record their estimate.

@@

```{r normsinpracticeitems}
practice_items = data.frame(
  "Practice" = c("Preregistration", "Registered reports", "p-hacking", "HARKing", "Info for replicability",
                 "Preprint", "open materials", "Open data", "Data on request", "Open access"),
  "Item" = c("The plan for collecting and analysing data for the study is posted in an online registry before data collection starts",
             "A plan for the study is submitted to a journal to be checked by experts (peer reviewed) before the data is collected and analysed",
             "The researchers run many different analyses of the data, and report only those that produce interesting findings",
             "The researchers describe their results as if they predicted those results from the beginning, even if that isn’t actually true",
             "The researchers provide enough practical detail in their written report that another researcher could fully repeat (replicate) their study without needing to ask any questions of the original researchers",
             "A manuscript describing the findings of the study is posted openly online as soon as it is complete, even if the manuscript has not yet been checked by experts (peer reviewed) and accepted for publication in a journal",
             "The written materials and measures for the study are posted openly online so that other researchers and members of the public can access and use them",
             "Once the study is published, the anonymous responses from participants are posted openly online so that anyone can access and use the responses in their own research",
             "Once the study is published, the anonymous responses from participants are available to other researchers on request",
             "The research report describing the study and its findings is published in a journal that is free for anyone to access")
)

@@

Participants' beliefs about the replicability of results in psychological science were indexed by two questions. The first asked participants to,

> "Imagine that a set of researchers selected 100 published studies about psychology, and repeat each study again, exactly how it was described in the original report but with a new set of participants. We call repeating a study like this a 'replication study.' At a guess, how many of these replication studies do you think would produce the same conclusions as the original studies?”

@@

In line with our preregistered analysis plan, we calculated the difference in means
between responses to each norm item and its accompanying counternorm, along with 
95% confidence intervals. For this analysis, we removed three cases with missing values. 
Table \@ref(tab:differencebetweennormandcounternorm) displays the means and standard deviations for each norm, counternorm, and the difference values.

@@

```{r differencebetweennormandcounternorm}

@@

practice_means_corr$Practice <- c("Critical thinking", "HARKing", "Info for replicability", "Open access", "Open data", "Open materials", "p-hacking", "Preprint", "Preregistration", "Registered reports")

# breadcrumbs:
# need to figure out whether I can rotate a page in papaja
# I need to use apa_tables.... (in line with papaja)
# EK - You can rotate the table, but I don't think it will rotate the page and it won't
# carry over into word

@@

<!-- I imagine we will remove the p.value column, but we might want this for now.  -->
<!-- It's not clear which stat the pvalue relates to, I would support removing it  -->

## Norms in practice
Participants were also asked to estimate the proportion of psychology studies globally that apply each of ten practices (see Table \@ref(tab:normsinpractice)). For many of these practices, participants’ estimates were near the midpoint of 50%. This said, participants perceived some practices as being applied relatively infrequently: For example, the mean estimate of the prevalence of HARKing, preprint sharing before publication, and open data sharing were all near 30%. Participants perceived the most common practice was providing enough information in written reports to permit replication without asking any questions of the original researchers.

```{r normsinpractice}

@@

in_practice_means$Practice <- c("Data on request", "Info for replicability", "HARKing", "p-hacking", "Open access", "Open data", "Open materials", "Preprint", "Pre-registration", "Registered report")

@@

Participants' estimates of the replicability of psychological studies were variable. The mean, _M_ =`r mean(df$rep_perc, na.rm = TRUE)` was near the midpoint of 50%, but with substantial variability around this estimate, _SD_ = `r sd(df$rep_perc, na.rm = TRUE)`, minimum = `r min(df$rep_perc, na.rm = TRUE)`,  maximum = `r max(df$rep_perc, na.rm = TRUE)`. A histogram of participants' responses is provided in Figure \@ref(fig:repperchistogram).

```{r repperchistogram, fig.cap="Histogram of participants' responses to the question: \"Imagine that a set of researchers select 100 published studies about psychology, and repeat each study again, exactly how it was described in the original report but with a new set of participants. We call repeating a study like this a \"replication study\". At a guess, how many of these replication studies do you think would produce the same conclusions as the original studies?\" Responses provided on a visual slider."}
hist(df$rep_perc, main = NULL, xlab = "Percentage")
```

@@

Figure A displays the histograms for each of the norms in practice items.

```{r normsinpracticehistogram}

practice_labels <- c(
  available_data = "Data on\nrequest",
  detailed_methodology = "Info\nrequired\nfor replication",
  harking = "HARKing",
  incomplete_results = "p-hacking",
  open_access = "Open access",
  registered_reports = "Registered reports",
  open_data = "Open data",
  open_materials = "Open\nmaterials",
  preprint_pre = "Preprints",
  preregistration = "Preregistration",
  registered_report = "Registered\nreport"
)

in_prac_long %>%
  ggplot(aes(x = `prevalence rating`)) +
  geom_histogram(aes(y=stat(count)), binwidth = 10) +
    xlab("Prevalence Ratings (%)") +
    ylab("Frequency") +
    theme_classic () +
    theme(axis.text = element_text(size = 9), axis.title = element_text(size = 9)) +
    facet_wrap(~practice, nrow = 2, labeller = labeller(practice = practice_labels))

#[breadcrumb: need to update the theme]

```
*Figure A*

@@

<!-- This is nice to do, but it generate a 150+ word paragraph of citations to packages, including citations to packages our code doesn't directly use (e.g. nlme, multilevel, etc.). We might need to cut it down manually to a more concise list?

EK: You can edit the r-refs bib directly to remove the packages that are just dependencies
-->
